### 2020-06-19 manuscript.rmd
Update manuscript.

@@

## Data Availability  
Deidentified data, as well as analysis scripts and model code are available at github.com/bjkellyio.

@@

#### Setting & Participants  
Subjects were recruited from the medical intensive care unit of an academic medical center.

>>>>

## Word Count

@@

## Data Availability  
Deidentified data, as well as analysis scripts and model code are available at github.com/bjklab.

@@

#### Setting & Participants  
Critically ill subjects were recruited from the medical intensive care unit of an academic medical center.
